### 2017-10-05 Sections/network_topologies.tex
Fixed graphic sizes, added stubs for QEC, added quantum Stockmarket, minor tweaks
Global spellcheck

\begin{figure}[!htb]
\includegraphics[width=0.7\columnwidth]{K_15}
\caption{The 15-vertex complete graph, $K_{15}$. Every vertex has an edge to every other, with a total of 105 edges.} \label{fig:complete_graph}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.7\columnwidth]{lattice}
\caption{A \mbox{$10\times 11$} square lattice graph, and how it might represent a network topology with geographically associated costs. Notice that Hobart has no internet connection (why even include Tasmania at all?).} \label{fig:lattice}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.75\columnwidth]{tree_3_8} \\
\includegraphics[width=0.75\columnwidth]{tree_4_8} \\
\includegraphics[width=0.75\columnwidth]{tree_5_8}
\caption{Balanced tree graphs with branching factor $b=8$, and depths $d=3,4,5$ (top to bottom). Despite having no redundant paths, the hierarchical structure of balanced trees somewhat resembles that of real-world networks, which are typically decomposed into a pyramid scheme of progressively smaller subnetworks.} \label{fig:tree_example}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{random_tree_1} \\
\includegraphics[width=\columnwidth]{random_tree_2}
\caption{Random trees with different randomised branching parameters (higher $b$ at bottom). When a node has zero branches, it terminates the branch. This type of graph topology qualitatively captures the hierarchical, yet ad hoc qualities of many real-world networks, and may act as a useful test model for simulations.} \label{fig:random_tree}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.8\columnwidth]{mst}
\caption{A random graph (blue) with an MST highlighted (red).} \label{fig:mst}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.6\columnwidth]{random_0}
\includegraphics[width=0.6\columnwidth]{random_05}
\includegraphics[width=0.6\columnwidth]{random_1}
\caption{The 15-vertex randomly-connected graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\text{edge}=0,0.5,1$} (top to bottom).} \label{fig:random_graph}
\end{figure}

@@

%
% The Internet Webgraph
%

\subsection{The internet webgraph} \index{Internet webgraph}

Of course, all the topological structures described until now are in-principle constructs. Of most relevance is the \textit{Webgraph}, the graph of the actual internet (or some other real-world network). Fig.~\ref{fig:webgraph} illustrates some example webgraphs. The combination of random, densely and sparsely connected, and tree structures, and its clear hierarchy are all evident. This encourages our intuition of the different types of structures present in realistic networks.

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{webgraph_1} \\
\includegraphics[width=\columnwidth]{webgraph_2}
\caption{Examples of real-world webgraphs, capturing their high-level random tree-like structure. Graphics attributed to the Center for Applied Internet Data Analysis (CAIDA), \texttt{\href{http://www.caida.org}{http://www.caida.org}}.} \label{fig:webgraph}
\end{figure}

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{K_15}
\caption{The 15-vertex complete graph, $K_{15}$. Every vertex has an edge to every other, with a total of 105 edges.} \label{fig:complete_graph}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{lattice}
\caption{A \mbox{$10\times 11$} square lattice graph, and how it might represent a network topology with geographically associated costs. Notice that Hobart has no internet connection (why even include Tasmania at all?).} \label{fig:lattice}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.375\textwidth]{tree_3_8} \\
\includegraphics[width=0.375\textwidth]{tree_4_8} \\
\includegraphics[width=0.375\textwidth]{tree_5_8}
\caption{Balanced tree graphs with branching factor $b=8$, and depths $d=3,4,5$ (top to bottom). Despite having no redundant paths, the hierarchical structure of balanced trees somewhat resembles that of real-world networks, which are typically decomposed into a pyramid scheme of progressively smaller subnetworks.} \label{fig:tree_example}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{random_tree_1} \\
\includegraphics[width=0.47\textwidth]{random_tree_2}
\caption{Random trees with different randomised branching parameters (higher $b$ at bottom). When a node has zero branches, it terminates the branch. This type of graph topology qualitatively captures the hierarchical, yet ad hoc qualities of many real-world networks, and may act as a useful test model for simulations.} \label{fig:random_tree}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{mst}
\caption{A random graph (blue) with an MST highlighted (red).} \label{fig:mst}
\end{figure}

@@

\begin{figure*}[!htb]
\includegraphics[width=0.32\textwidth]{random_0}
\includegraphics[width=0.32\textwidth]{random_05}
\includegraphics[width=0.32\textwidth]{random_1}
\caption{The 15-vertex randomly-connected graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\text{edge}=0,0.5,1$} (top to bottom).} \label{fig:random_graph}
\end{figure*}

@@

%
% The Internet Web-Graph
%

\subsection{The internet web-graph} \index{Internet web-graph}

Of course, all the topological structures described until now are in-principle constructs. Of most relevance is the \textit{Web-graph}, the graph of the actual internet (or some other real-world network). Fig.~\ref{fig:webgraph} illustrates some example web-graphs. The combination of random, densely and sparsely connected, and tree structures, and its clear hierarchy are all evident. This encourages our intuition of the different types of structures present in realistic networks.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{webgraph_1} \\
\includegraphics[width=0.47\textwidth]{webgraph_2}
\caption{Examples of real-world web-graphs of the internet, capturing their high-level random tree-like structure. Graphics attributed to the Center for Applied Internet Data Analysis (CAIDA), \texttt{\href{http://www.caida.org}{http://www.caida.org}}.} \label{fig:webgraph}
\end{figure}

### 2017-10-05 Sections/optical_encoding_of_quantum_information.tex
Fixed graphic sizes, added stubs for QEC, added quantum Stockmarket, minor tweaks
Global spellcheck

\begin{figure}[!htb]
\includegraphics[width=0.6\columnwidth]{pol_to_dual_conversion}
\caption{Conversion from single-photon polarisation encoding to dual-rail encoding, using a polarising beamsplitter (PBS) and wave-plate (WP). The PBS separates the polarisation components into two distinct spatial modes. The WP then rotates the polarisation of one of the spatial modes such that it has the same polarisation as the other. Conversion from dual-rail to polarisation encoding is just the reverse of this procedure.} \label{fig:pol_to_dual_conv}\index{Polarising beamsplitters}
\end{figure}

@@

Of course, the photon-number degree of freedom needn't be limited to 0 or 1 photons. By fully exploiting the photon-number degree of freedom, we can encode a qudit of arbitrary dimension into a single optical mode,
\begin{align} \label{eq:number_qudit}
\ket\psi_\text{qudit} \equiv \sum_{n=0}^\infty \alpha_n \ket{n}.
\end{align}
This may give the impression that a single optical mode has infinite information capacity. Needless to say, this sounds too good to be true, and it is. Loss decoheres photon-number-encoded states exponentially with photon-number, since for large photon-number the probability of a number state retaining its photon-number exponentially asymptotes to zero. So although in principle we can encode an $\infty$-level qudit, the moment any non-zero loss is introduced, this exponential dependence destroys the state (Sec.~\ref{sec:eff_err}).

@@

In time-bin encoding we define our basis of modes (whether it be qubits or higher-dimensional qudits) as distinct, non-overlapping time-bins, which are localised wave-packets in the temporal degree of freedom, each separated from the next by some fixed interval $\tau$. This can be considered a special case of spatio-temporal encoding, where the basis mode functions satisfy the relation,
\begin{align}
\xi_{j}(t) = \xi_0(t-j\tau),
\end{align}
as well as the usual orthonormality constraints. Here $\tau$ is sufficiently large, and $\xi_i(t)$ sufficiently temporally localised, that the temporal modes are orthogonal as per Eq.~(\ref{eq:spec_orth_def}).

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{pol_to_dual_conversion}
\caption{Conversion from single-photon polarisation encoding to dual-rail encoding, using a polarising beamsplitter (PBS) and wave-plate (WP). The PBS separates the polarisation components into two distinct spatial modes. The WP then rotates the polarisation of one of the spatial modes such that it has the same polarisation as the other. Conversion from dual-rail to polarisation encoding is just the reverse of this procedure.} \label{fig:pol_to_dual_conv}\index{Polarising beamsplitters}
\end{figure}

@@

Of course, the photon-number degree of freedom needn't be limited to 0 or 1 photons. By fully exploiting the photon-number degree of freedom, we can encode a qudit\footnote{A $d$-level system, as opposed to a qubit's two levels.}\index{Qudits} of arbitrary dimension into a single optical mode,
\begin{align} \label{eq:number_qudit}
\ket\psi_\text{qudit} \equiv \sum_{n=0}^\infty \alpha_n \ket{n}.
\end{align}
This may give the impression that a single optical mode has infinite information capacity. Needless to say, this sounds too good to be true, and it is. Loss decoheres photon-number-encoded states exponentially with photon-number, since for large photon-number the probability of a number state retaining its photon-number exponentially asymptotes to zero. So although in principle we can encode an $\infty$-level qudit, the moment any non-zero loss is introduced, this exponential dependence destroys the state (Sec.~\ref{sec:eff_err}).

@@

In time-bin encoding we define our basis of modes (whether it be qubits or higher-dimensional qudits\index{Qudits}) as distinct, non-overlapping time-bins, which are localised wave-packets in the temporal degree of freedom, each separated from the next by some fixed interval $\tau$. This can be considered a special case of spatio-temporal encoding\index{Spatio-temporal encoding}, where the basis mode functions satisfy the relation,
\begin{align}
\xi_{j}(t) = \xi_0(t-j\tau),
\end{align}
as well as the usual orthonormality constraints. Here $\tau$ is sufficiently large, and $\xi_i(t)$ sufficiently temporally localised, that the temporal modes are orthogonal as per Eq.~(\ref{eq:spec_orth_def}).
